An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-17 scagnostics.Rmd
Added short discussion of final example result.

We next investigate the dependence of the final result on the input starting plane. In particular if there are many local maxima the effect may be large, and many random starting planes may be needed to find a global maximum. To this end we first reduce the dataset dimensionality to include only two types of parameters: first, spin related parameters (i.e. alpha, theta\_jn, chi\_tot and chi\_p), and second position related parameters (i.e. ra, dec and distance). Note that this includes a number of variables for which we have established association and one dimensional structure above, i.e. ra and dec; chi\_tot and chi\_p; and theta\_jn. We generate a small set of random starting planes and optimise the splines2D index (it is prefered here over the TIC index as it is much more efficient to compute on large data sets). We compare six final views identified in this manner (i.e. differing only in randomly selected starting plane) in Fig. \ref{fig:bbhGuided3}. We note large variation in final views, only one of the six tries identified the view of ra vs dec. \textcolor{red}{list corresponding index values for each plot, maybe in the caption.}

@@

Indeed the TIC index guided tour found an informative view between the three parameters time, ra and dec whithin the full datase (after once again removing the second mass parameter, see explanation above), which is not described by a function. We can approximate it by showing the sum of the rescaled ra and dec variable against time, or when using the original parameter values by approximate scaling, see Figure \ref{fig:bbhRes}, but clearly the view in Fig. \ref{fig:bbhGuided} has higher TIC score.

\textcolor{red}{Things to add here: comparison of final projection matrices for all three, comparison of index evolution between the three index functions over the TIC guided tour path, plotly animation of the guided tour (check with Nick S. about function to readily to this)}

>>>>

We next investigate the dependence of the final result on the input starting plane. In particular if there are many local maxima the effect may be large, and many random starting planes may be needed to find a global maximum. To this end we first reduce the dataset dimensionality to include only two types of parameters: first, spin related parameters (i.e. alpha, theta\_jn, chi\_tot and chi\_p), and second position related parameters (i.e. ra, dec and distance). Note that this includes a number of variables for which we have established association and one dimensional structure above, i.e. ra and dec; chi\_tot and chi\_p; and theta\_jn. We generate a small set of random starting planes and optimise the splines2D index (it is prefered here over the TIC index as it is much more efficient to compute on large data sets). We compare six final views identified in this manner (i.e. differing only in randomly selected starting plane) in Fig. \ref{fig:bbhGuided3}. We note large variation in final views, only one of the six tries identified the view of ra vs dec, which however clearly has the maximum index value amongst all views. \textcolor{red}{add axes to plot, then we can make statement about how "far" the other views are from the "best" one.}

Finally, given the results above, it makes sense to also consider smaller parameter-subspaces to look for stronger association. (A procedure to first scout the parameter space for large index values is not efficent in this case because of the strong dependence on rotation angles in this paricular setup.) One subspace for which we found strong association between three variables is using the randomly selected parameter set (m1, ra, chi\_tot, alpha, distance, dec). Optimising again the splines2D index value allows us to find the final view shown in Figure \ref{constructedExample} (left), which we can reproduce from the original parameters as shown in the middle (here we work with the rescaled parameter values), as a combination of the position parameters ra and dec with the spin parameter alpha. For comparison we also show the dependence between ra and dec only, which is fuzzy compared to the ideal view identified by the PP optimisation. \textcolor{red}{This result is unexpected, it can be understood from ?????}

@@
